%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Daniel McGrath} % Your name
%\address{Conshohocken, PA}
\address{daniel.mcgrath9@gmail.com} % Your phone number and email
\address{https://danielmcgrath.xyz \\ https://github.com/djm158} % \\ https://www.linkedin.com/in/djmcg/}

\begin{document}

%----------------------------------------------------------------------------------------
%	PROFESSIONAL SUMMARY SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Professional Summary}
Senior Frontend Engineer with 7 years of experience specializing in React, Next.js, and scalable frontend architecture. Proven track record of enhancing UX and performance for Fortune 500 e-commerce platforms. Passionate about open-source contributions, mentoring developers, and driving best practices in frontend development.
\end{rSection}



%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Experience}
\begin{rSubsection}{Nearform}{June 2022 - Present}{Senior Software Engineer}{Remote}
\item Designed and implemented end-to-end features for large e-commerce clients using Next.js and GraphQL.
\item Facilitated a transition from Angular to React/Next.js, focusing on a redesign of navigation menu with Tailwind and Zustand, leading to improved user experience and engagement.
\item Established frontend best practices and mentored junior engineers, fostering team growth and efficiency.
\item Actively contributed to open-source projects, sharing best practices and improving community adoption.
\end{rSubsection}

\begin{rSubsection}{WizeHive}{September 2020 - June 2022}{Software Engineer}{Conshohocken, PA}
\item Built a new grant management platform from scratch, streamlining application processing and user workflows.
\item Developed an interactive workflow builder using React flow and Apollo GraphQL, improving user efficiency and usability.
\item Addressed key user pain points, improving the overall user experience and satisfaction.
\item Optimized application performance, ensuring a faster and more reliable platform for end-users.
\end{rSubsection}

\begin{rSubsection}{Vistar Media}{September 2018 - September 2020}{Software Engineer}{Philadelphia, PA}
\item Developed UI features for digital out of home ad-tech platform using TypeScript, React, and Redux
\item Built and maintained REST APIs using Python and Flask, improving data retrieval and application responsiveness.
\item Deployed and monitored microservices with AWS and Datadog, enhancing system reliability.
\end{rSubsection}

\begin{rSubsection}{Computer Enterprises Inc}{Jan 2018 - September 2018}{Associate Developer}{Plymouth Meeting, PA}
\item Leveraged Azure Batch, Microsoft R Open to deploy massively parallel R application to Azure Cloud
\item Developed insurance policy web application using Web Components
\end{rSubsection}


\end{rSection}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Education}

    {\bf University of Pittsburgh} \hfill {December 2017} \\
    B.S. in Computer Engineering \\
    \textit{Summa Cum Laude} \\
    Overall GPA: 3.8
    
    \end{rSection}
%----------------------------------------------------------------------------------------
%	TECHNICAL SKILLS SECTION
%----------------------------------------------------------------------------------------
\pagebreak
\begin{rSection}{Technical Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Programming Languages & JavaScript, TypeScript, Python, HTML5, CSS/SASS \\
Frameworks & React, Next.js, Tailwind, Node.js, GraphQL, Apollo, \\
Databases & PostgreSQL, MySQL, MongoDB \\
Tools \& Testing & React Testing Library, Git, Docker, microservices \\
Cloud Platforms & AWS, Azure \\
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
